General constraints on magic distillation protocols from statistical mechanics

### 2021-04-19 appendix.tex
made the changes discussed, havent calculated thauma yet

In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1} = (\frac{1}{n},\dots,\frac{1}{n})$.
This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
\begin{proposition}\label{prop:major}
Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
 \begin{enumerate}
	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
\end{theorem}
	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
 \end{enumerate}
\end{proposition}
	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.

@@

\begin{proposition}\label{prop:rmajor}
Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
  \begin{enumerate}
    \item[(i)] $\bmx \prec_{\r} \bmy$;
    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - t r_i} \leq \sum\limits_{i=1}^n \abs{y_i - t r_i}$ for all $t \in \mathbb{R}$;
    \item[(iv)] $\sum\limits_{i=1}^n (x_i - t r_i)^+ \leq \sum\limits_{i=1}^n (y_i - t r_i)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
  \end{enumerate}
\end{proposition}
\begin{proof}$ $\vspace{-12pt}\\
\begin{enumerate}
	\item[1$\leftrightarrow2$]
	Suppose there exists a $\r$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1}$.
$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\r} \circ A) (\r) = \Gamma_{\r}(\r) = \frac{1}{N}\bm{1}$. Then, $B$ maps $\Gamma_{\r}({\bmy})$ to $\Gamma_{\r}({\bmx})$.

	Conversely, given $B$, let $A = \Gamma_{\r}^{-1} \circ B \circ \Gamma_{\r}$.
	Similarly, $A$ is a $\r$--stochastic matrix that maps $\bmy$ to $\bmx$.
	\item[$2\leftrightarrow3$] These \hspace{1pt} three \hspace{1pt} statements \hspace{1pt} are \hspace{1pt} equivalent \hspace{1pt} to \hspace{1pt} state-
	\item[$2\leftrightarrow4$] \vspace{-7pt} ments (iii), (iv), (v) \hspace{1pt} in~\cref{prop:major} respectively, 
	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\r}({\bmx}), \Gamma_{\r}({\bmy})$, which becomes apparent by rewriting
	\begin{align*}
	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - t r_i} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - t r_i)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
	&\hspace{15pt} L_{\bmx|\r}(t) = L_{\Gamma_{\r}(\bmx)}(t),
	\end{align*} 
and similarly for the right hand sides of the inequalities.
\end{enumerate}
\vspace{-19pt}
\end{proof}

>>>>

In the unital fragment, namely the limit of infinite temperature, $\beta = 0$, the free state is the maximally mixed state $\frac{1}{n}\id$ with uniform Wigner distribution $\frac{1}{n}\bm{1} = (\frac{1}{n},\dots,\frac{1}{n})$.
This fragment is governed by simple majorization and we first prove strong equivalences for this type of majorization.
\begin{proposition}\label{prop:major}
Given $\bmx, \bmy \in \mathbb{R}^n$ the following statements are equivalent:
 \begin{enumerate}
	\item[(i)]\label{en:m1} $\bmx \prec \bmy$;
	\item[(ii)]\label{en:m2} $\bmx = B \bmy$ for bistochastic $B$;
	\item[(iii)]\label{en:m3} $\sum\limits_{i=1}^n \abs{x_i - t} \leq \sum\limits_{i=1}^n \abs{y_i - t}$ for all $t \in \mathbb{R}$;
	\item[(iv)]\label{en:m4} $\sum\limits_{i=1}^n (x_i - t)^+ \leq \sum\limits_{i=1}^n (y_i - t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$, where $(x)^+ = \max{\{x, 0\}}$;
	\item[(v)]\label{en:m5} $L_{\bmx}(t) \leq L_{\bmy}(t)$ for $t\in [0,1)$	and \vspace{5pt}\\ $L_{\bmx}(1) = L_{\bmy}(1)$, where $L_{\bmz}(t) = L_{\bmz|\frac{1}{n}\bm{1}}(t)$.
 \end{enumerate}
\end{proposition}
	The equivalence between (i) and (ii) is the statement of the Hardy, Littlewood and Polya theorem and is taken as our definition of majorisation in the main text.

@@

\begin{proposition}\label{prop:rmajor}
Given $\bmx, \bmy, \r \in \mathbb{R}^n$, such that the components of $\r$ are positive, the following statements are equivalent:
  \begin{enumerate}
    \item[(i)] $\bmx \prec_{\r} \bmy$;
    \item[(ii)] $\Gamma_{\r}({\bmx}) \prec \Gamma_{\r}({\bmy})$;
    \item[(iii)]\label{en:tm3} $\sum\limits_{i=1}^n \abs{x_i - r_i t} \leq \sum\limits_{i=1}^n \abs{y_i - r_i t}$ for all $t \in \mathbb{R}$;
    \item[(iv)] $\sum\limits_{i=1}^n (x_i - r_i t)^+ \leq \sum\limits_{i=1}^n (y_i - r_i t)^+$ for all $t \in \mathbb{R}$ and \vspace{5pt}\\ $\sum\limits_{i=1}^n x_i = \sum\limits_{i=1}^n y_i$;
    \item[(v)] $L_{\bmx|\r}(t) \leq L_{\bmy|\r}(t)$ for $t\in [0,1)$ and \vspace{5pt}\\ $L_{\bmx|\r}(1) = L_{\bmy|\r}(1)$.
  \end{enumerate}
\end{proposition}
\begin{proof}$ $\vspace{-12pt}\\
\begin{enumerate}
	\item[1$\leftrightarrow2$]
	Suppose there exists a $\r$--stochastic $A$ such that $\bmx = A\bmy$ and let $B = \Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1}$.
$B$ is a $N$--dimensional bistochastic matrix, since composition of stochastic matrices is stochastic and $(\Gamma_{\r} \circ A \circ \Gamma_{\r}^{-1})\big(\frac{1}{N}\bm{1}\big) = (\Gamma_{\r} \circ A) (\r) = \Gamma_{\r}(\r) = \frac{1}{N}\bm{1}$. Then, $B$ maps $\Gamma_{\r}({\bmy})$ to $\Gamma_{\r}({\bmx})$.

	Conversely, given $B$, let $A = \Gamma_{\r}^{-1} \circ B \circ \Gamma_{\r}$.
	Similarly, $A$ is a $\r$--stochastic matrix that maps $\bmy$ to $\bmx$.
	\item[$2\leftrightarrow3$] These \hspace{1pt} three \hspace{1pt} statements \hspace{1pt} are \hspace{1pt} equivalent \hspace{1pt} to \hspace{1pt} state-
	\item[$2\leftrightarrow4$] \vspace{-7pt} ments (iii), (iv), (v) \hspace{1pt} in~\cref{prop:major} respectively, 
	\item[$2\leftrightarrow5$] \vspace{-7pt} for the embedded vectors $\Gamma_{\r}({\bmx}), \Gamma_{\r}({\bmy})$, which becomes apparent by rewriting
	\begin{align*}
	&\hspace{15pt} \sum\limits_{i=1}^n \abs{x_i - r_i t} = \sum\limits_{i=1}^n r_i \abs{\frac{x_i}{r_i} - t} = \sum\limits_{i=1}^N \abs{\Gamma_{\r}(\bmx)_i - t}, \\[3pt]
	&\hspace{15pt} \sum\limits_{i=1}^n (x_i - r_i t)^+ = \sum\limits_{i=1}^N (\Gamma_{\r}(\bmx)_i - t)^+ \text{ and} \\[6pt]
	&\hspace{15pt} L_{\bmx|\r}(t) = L_{\Gamma_{\r}(\bmx)}(t),
	\end{align*} 
and similarly for the right hand sides of the inequalities.
\end{enumerate}
\vspace{-19pt}
\end{proof}
